---
title: "Manual"
author: "Hendrik Pehlke"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
--------------------------------------------------------------------------------
The development of the **'CoordFixR'** R-package is a result of the [**CoastCarb**](https://coastcarb.eu/) programme, funded under the European Union's Horizon 2020 research and innovation programme under Marie Skłodowska-Curie Grant Agreement No 872690.
--------------------------------------------------------------------------------


## Summary

The package 'CoordFixR' calculates or converts coordinates from (almost) all possible notations into decimal degrees. 

It does not matter whether characters or letters for degrees, minutes or seconds are included (e.g. “°” or “degree”), whether spaces, underscores or slashes occur, or whether designations such as “North”, “South”, “West” or “East” or minus signs (“-”) are included. 

Coordinates that contain text components such as 'degrees', 'minutes' or 'seconds' are also correctly converted to decimal degree notation without any problems.

## Installation

To install the app from GitHub you have to install the package 'devtools' first.

```{r install, eval=F, echo=T}
install("devtools") # if the package 'devtools' is not already installed on your device

# install the development version of the package 'CoordFixR' from GitHub
devtools::install_github("HP-AWI/CoordfixR")
```


## Load the package 'CoordFixR' into R

After having successfully installed the package 'CoordFixR' you have to load it in R.

```{r}
# library(CoordFixR)
```


## Start the app

You run the app just type the following command:

```{r run app, eval=F, echo=T}
# start the app
CoordfixR::launch_app()
```
